---
title: "IDS investigation worksheet"
author: "by Team-Name: User1, User2, User3, User4 & User5"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, message = FALSE}
# packages
library(tidyverse)
library(ggplot2)
library(readODS) # data is not excel its .ods

```


```{r load-data}
# data 
Annual_Data <- ods_sheets("data/Population_30June2023_annual.ods") %>%
  set_names() %>% # for different names
  map(~ read_ods("data/Population_30June2023_annual.ods", sheet=.x))
```

```{r clean-data}
# Visualising data and cleaning data

#data cleaning for sheet 1
Annual_Data_A1_3b <- Annual_Data[[5]]

Date_A1_3b <- as.character(Annual_Data_A1_3b[1,])

colnames(Annual_Data_A1_3b) <- Date_A1_3b

Annual_Data_A1_3b <- Annual_Data_A1_3b[-1, ]

colnames(Annual_Data_A1_3b)[1]<-"anything"

Annual_Data_A1_3b

Annual_Data_A1_3b <- Annual_Data_A1_3b %>%
  slice(1,15,29,43)


#selects A1.1, makes a new variable that is the dates when checked, replace the column names using the dates

print(Annual_Data_A1_3b)
  
  
```
