---
title: "IDS investigation worksheet"
author: "by Team-Name: User1, User2, User3, User4 & User5"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, message = FALSE}
# packages
library(tidyverse)
library(ggplot2)
library(readODS) # data is not excel its .ods

```


```{r load-data}
# data 
Annual_Data <- ods_sheets("data/Population_30June2023_annual.ods") %>%
  set_names() %>% # for different names
  map(~ read_ods("data/Population_30June2023_annual.ods", sheet = .x))

#this takes a while and ignore the Name "names:New names:..." will fix later
#22 data sheets  2-23 are data
#needs cleaning, eg sheet 23 (A1_18)) columns are not correct the tiles are the original name then 2,3,4... and the date is in character form as a variable, each sheet needs cleaning in different ways
```

```{r clean-data}
# Visualising data and cleaning data

#data cleaning for sheet 1
Annual_Data_A1_1 <- Annual_Data[[2]]

Date_A1_1 <- as.character(Annual_Data_A1_1[1, ])

colnames(Annual_Data_A1_1) <- Date_A1_1

Annual_Data_A1_1 <- Annual_Data_A1_1[-1, ]
             
#selects A1.1, makes a new variable that is the dates when checked, replace the column names using the dates

print(Annual_Data_A1_1)
  
  
```
